%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutBold}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingWithoutLocation}[3]{
  \vspace{-1pt}\item
  \begin{tabular}
    \textbf{#1} & #2 & #3
  \end{tabular}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\definecolor{link-blue}{rgb}{51,102,187}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Taksh Singh}} & Email : \href{mailto:taksh001@gmail.com}{taksh001@gmail.com}\\
  \href{https://taksh.dev}{https://taksh.dev} & Mobile : +1-217-706-4906 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois, Urbana-Champaign}{Champaign, IL}
      {Bachelor of Science in Computer Science;  GPA: 3.88}{Aug 2019 -- May 2023}
      \resumeItemListStart
        \resumeItem{Coursework}
        {Systems Programming, Probability and Statistics for Computer Science, Data Structures and Algorithms, Computer Architecture, Linear Algebra, Discrete Structures}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rubrik}{Remote}
      {Software Engineering Intern}{May 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItemWithoutBold
          {Decreased downtime during weekly upgrade for Rubrik Polaris by 20\%, by selectively deploying certain container images before maintenance window through runtime checks, pushing us closer to the product's availability goal of 99.5\% uptime.}
        \resumeItemWithoutBold
          {
            Fixed scalability bug in stress-testing framework, allowing users to run an accelerated simulation for upto 25000 VMs instead of just 1 VM earlier, by debugging the problem by analyzing memory dumps generated using through pprof.
          }
        \resumeItemWithoutBold
        {
            Created performance benchmarks for stress-testing framework by writing an automated script that took periodic memory snapshots, allowing teams to estimate in advance how much memory to reserve for tests.
        }
      \resumeItemListEnd
      
    \resumeSubheading
      {Rubrik}{Remote}
      {Software Engineering Intern}{Jan 2021 - May 2021}
      \resumeItemListStart
        \resumeItemWithoutBold
        {
            Reduced runtime of a long-running periodic job by 85\% from 7 days to 1 day, by parallelizing its implementation using a map-reduce inspired framework.
        }
        \resumeItemWithoutBold
        {
            Increased performance and reduced failure rate for distributed job framework, by overhauling its throttling architecture, allowing resources to be used more efficiently.
        }
        \resumeItemWithoutBold
        {
            Increased productivity of support engineers by allowing them to deploy fixes to common bugs more quickly and diagnose problems, by adding command line tools to automate routine support operations in Rubrik clusters.
        }
        \resumeItemWithoutBold
        {
            Improved customer experience by adding alert to automatically detect certain fatal system anomalies to proactively alert Rubrik about them, without any customer intervention, so that they can be fixed even before the customer notices them.
        }
      \resumeItemListEnd

    \resumeSubheading
      {Hora}{Remote}
      {Software Engineer Intern}{Jun 2020 - Aug 2020}
      \resumeItemListStart
        \resumeItemWithoutBold
        {
            Created backend engine for a game (for about 20000 users) that tested user's language skills, awarded coins to them based on their performance, and tracked their history. Also wrote internal application to manually add questions to the game.
        }
        \resumeItemWithoutBold
        {
            Streamlined process of tracking performance of users across 2 apps, by developing a common micro-service to store their data and refactoring the existing codebase.
        }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \projectSubheading
        {Plasmafinder.com}{June 2020 - Present}
        \resumeItemListStart
            \resumeItemWithoutBold
            {
                Launched platform to match critically-ill COVID-19 patients with plasma donors for an experimental treatment, which processed more than 400 registrations. \href{https://github.com/TakshPSingh/plasmafinder.com}{\color{blue}{(link to repository)}}
            }
            \resumeItemWithoutBold
            {
                Implemented real-time matching algorithm that matched patients and donors in 10 seconds.
            }
        \resumeItemListEnd
    \projectSubheading
        {LaTeX resume to PDF}{July 2021 - Present}
        \resumeItemListStart
            \resumeItemWithoutBold
            {
                Created tool to automate the process of tracking LaTeX resume iterations using Git, rendering them into PDFs, and releasing them through a static link via a CI/CD pipeline. \href{https://github.com/TakshPSingh/latex-resume-to-pdf}{\color{blue}{(link to repository)}}
            }
            \resumeItemWithoutBold
            {
                Trivia: I built this tool while writing this resume.
            }
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, Scala, C/C++, Python, JavaScript}
     \hfill
     \textbf{Technologies}{: Docker, Kubernetes, Linux, Node.js}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
